\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-06-11 RO-MAN-2017-2/Parts/Introduction.tex
Reviewed

The development of fast, cheap, and reliable electronics has enabled the creation of new devices and versatile robotic platforms. These new platforms' capabilities have expanded the frontiers of the robots applications to new environments where robot are expected to interact with humans, such as health care, and house cleaning, among others. However, bringing robots in these environment raises the challenge to increase robots' acceptance. Although this could be seen as an easy task that just would need improvements in robots' appearance and capabilities, it is possible that people would expect to treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil this expectations.

Some researchers have suggested that embedding emotion expression capabilities in robots could improve their acceptance in social environments~\cite{Pavia2014}. To this purpose, some researchers~\cite{Breazeal2002, Arras2012} have added specific emotional poses and expression to their robots. Others have studied how to convey emotions with specific platforms~\cite{Li2011, Brown2014}. Nevertheless, these works have created modules to show emotions that are strongly integrated to their systems, which eliminate the possibility to re-use or adapt them for other projects.

>>>>

The development of fast, cheap, and reliable electronics has enabled the creation of new devices and versatile robotic platforms. These new platforms' capabilities have expanded the frontiers of the robotic applications to new environments, where robots are expected to interact with humans, such as health care and house cleaning, among others. However, bringing robots in these environments raises the challenge to increase robots' acceptance. Although this could be seen as an easy task that just would need improvements in robots' appearance and capabilities, it is possible that people would expect to treat robots as humans, like they do with computers.~\cite{Reeves1996}, which makes necessary the creation of robots able to fulfil these expectations.

Some researchers have suggested that embedding emotion expression capabilities in robots could improve their acceptance in social environments~\cite{Pavia2014}. To this purpose, some researchers (e.g.,~\cite{Breazeal2002, Arras2012}) have added specific emotional poses and expressions to their robots. Others have studied how to convey emotions with specific platforms~\cite{Li2011, Brown2014}. Nevertheless, these works have created modules to show emotions that are strongly integrated in their systems, which eliminate the possibility to re-use or adapt them for other projects.
